Generating Interactive WebSocket Applications in TypeScript

### 2020-03-03 PLACES_2020/casestudy.tex

\begin{figure}
\begin{lstlisting}[language=JavaScript, tabsize=4]
const handleP1Move: Receive_P1 = (move: Point) => {
	board.P1(move);			// User logic
	if (board.won()) { return [Labels.Lose, move, move]; }
	else if (board.draw()) { return [Labels.Draw, move, move]; }
	else { return [Labels.Update, move, handleP2Move]; }}

// Instantiate session - `handleP2Move` defined similarly
new NoughtsAndCrosses.Svr(webSocketServer, handleP1Move, handleP2Move);
\end{lstlisting}
\captionof{lstlisting}{Session runtime instantiation for \textit{Noughts and Crosses} \texttt{Svr}.}
\label{lst:svrprotocol}
\end{figure}

@@

\paragraph{Game server}
We set up the WebSocket server as an Express.js \cite{ExpressJS}
application on top of a Node.js \cite{NodeJS} runtime.
We define our own game logic in a \texttt{Board} class to keep track of the
game state and expose methods to query the result.
This custom logic is integrated into our \texttt{Receive\_P1} and
\texttt{Receive\_P2} handlers (\cref{lst:svrprotocol}), so the session runtime
can handle \texttt{Pos(Point)} messages from players and transition according
to the injected game logic.

>>>>

\begin{figure}
\begin{lstlisting}[language=JavaScript, tabsize=4]
const handleP1Move: S13 = (move: Point) => {
	board.P1(move);			// User logic
	if (board.won()) { return [Labels.Lose, move, move]; }
	else if (board.draw()) { return [Labels.Draw, move, move]; }
	else { return [Labels.Update, move, handleP2Move]; }}

// Instantiate session - `handleP2Move` defined similarly as S18
new NoughtsAndCrosses.Svr(webSocketServer, handleP1Move);
\end{lstlisting}
\captionof{lstlisting}{Session runtime instantiation for \textit{Noughts and Crosses} \texttt{Svr}.}
\label{lst:svrprotocol}
\end{figure}

@@

\paragraph{Game server}
We set up the WebSocket server as an Express.js \cite{ExpressJS}
application on top of a Node.js \cite{NodeJS} runtime.
We define our own game logic in a \texttt{Board} class to keep track of the
game state and expose methods to query the result.
This custom logic is integrated into our \texttt{handleP1Move} and
\texttt{handleP2Move} handlers (\cref{lst:svrprotocol}), so the session runtime
can handle \texttt{Pos(Point)} messages from players and transition according
to the injected game logic.

### 2020-03-03 PLACES_2020/intro.tex

We see the application of the MPST methodology to verifying interactive web
applications written in TypeScript to be an interesting design space -- to what
extent can the MPST methodology be applied such that we leverage TypeScript
language features to maximise static safety guarantees whilst preserving a
flexible, natural and idiomatic workflow for TypeScript developers?
Such a workflow would ultimately decrease the overhead for incorporating MPST
into mainstream web system, which reduces development time by programmatically
verifying communication correctness of the implementation.

>>>>

We see the application of the MPST methodology to verifying interactive web
applications written in TypeScript to be an interesting design space -- to what
extent can the MPST methodology be applied such that we leverage TypeScript
language features to maximise static safety guarantees whilst preserving a
flexible, natural and idiomatic workflow for TypeScript developers?
Such a workflow would ultimately decrease the overhead for incorporating MPST
into mainstream web development, which reduces development time by programmatically
verifying communication correctness of the implementation.
